---
title: Data Science Adventures
author: Winnie Yan
date: '2017-06-05'
slug: second-new-post-in-r-markdown
categories: []
tags: []

---

In the fleeting first week of classes, we explored the basics of R, including creating vectors and indexing. Please have a look at the following examples we've done in class...

```{r}
#Create a vector with the first 10 elements of the Fibonacci Sequence.
fibonacci_sequence <- c(1,1,2,3,5,8,13,21,34,55)
#Extract the seventh element of the sequence.
fibonacci_sequence[7]
#Extract the odd numbers from the sequence.
fibonacci_sequence[c(1,2,4,5,7,8,9,10)]
#Extract the numbers at odd numbered positions
fibonacci_sequence[seq(from = 1, to = 9, by = 2)]
fibonacci_sequence[rep(c(T,F),5)]

```

We also looked at a very useful RPackage, ggplot2. With the help of ggplot2, we were able to create different kinds of plots for different data sets. Here is a plot I made for the dataset "mtcars" comparing horsepower and 1/4 mile time.

```{r}
library(ggplot2)
ggplot(data = mtcars, aes(x=qsec, y=hp)) + geom_point(alpha = 0.5, color= "red") + geom_smooth(method = lm)
```


We then moved onto writing functions in R. This is very helpful for our project this week, which is creating a R package. For homework, I wrote a function that generates the Fibonacci sequence. 

```{r}
fibo_generator <- function(n) {
  if (n<=0) stop("Must be positive")
  x = numeric(n)
  x[1:2] = c(1,1)
  if (n==1) return(x[1])
  else if (n==2) return(x)
  for (i in 3:n) {
    x[i] = x[i-1] + x[i-2]
  }
  return(x)
}

##trials
fibo_generator(5)
fibo_generator(14)
```


Our group is hoping to make a R package that focuses on the famous Bayes' Theorem. Stay tuned!